---
title: SHOULD PERSONALIZATION BE OPTIONAL ON PAID STREAMING PLATFORMS? VALUE OF USER
  DATA FOR PERSONALIZATION IN PAID STREAMING PLATFORMS AS AN INDIRECT COMPENSATION
author: "Bengusu Ozcan"
date: "12/19/2021"
output:
  html_document: default
  word_document: default
note: For the data files and reference on which short variable names stand for which
  fields, refer to https://github.com/bengusuozcan/personalization_experiment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Please install necessary packages as below if not installed yet
#install.packages("dplyr")
#install.packages("tidyverse")
#install.packages("ggplot2")
#install.packages("gt")
#install.packages("psych")
#install.packages("texreg")
#install.packages("stargazer")
#install.packages("broom")
library(broom)
library(stargazer)
library(texreg)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(gt)
library(doBy)
library(psych)
```

**Data Ingestion**

```{r}
#read Cleaned_Modified_Substituted_Personalization_Preferences_12-18-21-Qualtrics.csv from your local drive
data <- read.csv(file.choose())
```

```{r}
#separate data into control and treatment groups. will be used in some of the analyses. 
data_control <- data %>% filter(group=='control')
data_treatment <- data %>% filter(group=='treatment')
```

**Demographics**

```{r}
#General Demographics
#Values in Table1
data %>% group_by(group) %>% summarise(max=max(Age),min=min(Age),avg=mean(Age),med=median(Age))
data %>% summarise(max=max(Age),min=min(Age),avg=mean(Age),med=median(Age))
table(recoded$Gender,recoded$group)
table(recoded$Education,recoded$group)
table(recoded$Income,recoded$group)
table(recoded$Political,recoded$group)
```

```{r}
#Platform Demographics
#reading tokenized platforms data, Modified_Platforms_Used_Personalization_Preferences_12-18-21-Qualtrics.csv
platforms=read.csv(file.choose())
```

```{r}
#Figure 3 data manipulation to include "all others"
#Which PSPs Do the Participants Use in Real Life?
platforms2 <- platforms %>% group_by(Platforms) %>% filter(Platforms != "All of the above") %>% summarize(count=n()+1)
platforms2 %>% ggplot(aes(x=reorder(Platforms,count),y=count))+geom_bar(stat='identity',position='dodge')+labs(y = "Number of people")+
  theme_minimal()+scale_fill_grey()+
    geom_text( aes(label = count),colour = "black", size = 3, vjust = 0.3, hjust=-0.2, position = position_dodge(.8))+theme(axis.title.y=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank())+coord_flip()
```
```{r}
#Figure4, participants Using only One PSP
platforms %>% filter(Using_PSPs==1) %>% group_by(Platforms) %>% summarize(count=n()) %>% 
ggplot(aes(x=reorder(Platforms,count),y=count))+geom_bar(stat='identity',position='dodge')+labs(y = "Number of people")+
  theme_minimal()+scale_fill_grey()+
    geom_text(
    aes(label = count),
    colour = "black", size = 3,
    vjust = 0.3, hjust=-0.2, position = position_dodge(.8)) + theme(axis.title.y=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank())+coord_flip()
```


**Summary statistics for main dependent variables**

```{r}
data %>% group_by(group) %>% summarize(count=n(),avg=mean(fee), sd=sd(fee))
data %>% group_by(group) %>% summarize(count=n(),avg=mean(Personalization_fee_difference), sd=sd(Personalization_fee_difference))
describe(data$fee)
describe(data_control$fee)
describe(data_treatment$fee)
describe(data$Personalization_fee_difference)
describe(data_control$Personalization_fee_difference)
describe(data_treatment$Personalization_fee_difference)
describe(data$Fee_personalization)
describe(data_control$Fee_personalization)
describe(data_treatment$Fee_personalization)
describe(data$Fee_without_personalization)
describe(data_control$Fee_without_personalization)
describe(data_treatment$Fee_without_personalization)
```

```{r}
#Variance of main dependent variables
var(data$fee)
var(data_control$fee)
var(data_treatment$fee)
var(data$Personalization_fee_difference)
var(data_control$Personalization_fee_difference)
var(data_treatment$Personalization_fee_difference)
var(data$Fee_personalization)
var(data_control$Fee_personalization)
var(data_treatment$Fee_personalization)
var(data$Fee_without_personalization)
var(data_control$Fee_without_personalization)
var(data_treatment$Fee_without_personalization)
```


**Hypothesis Testing**

1) Hypothesis A

Normality test 

```{r}
#D1 is not normally distributed
shapiro.test(data$fee)
```

F-test for equal variances

```{r}
#there is no significant difference between the variances of D1 between the two sets of data
ftest1 <- var.test(fee ~ group, data = data)
ftest1
```

2 sample t-test
```{r}
#No statistically significant difference between control and treatment groups for D1
HA_ttest <-t.test(fee ~ group, data = data, var.equal=TRUE)
HA_ttest
```

2) Hypothesis B


Normality test on D2
```{r}
#D2 is not normally distributed
shapiro.test(data$Personalization_fee_difference)
```
Normality test on D3
```{r}
#D3 is not normally distributed
shapiro.test(data$Fee_personalization)
```
Normality test on D4
```{r}
#D4 is not normally distributed
shapiro.test(data$Fee_without_personalization)
```

F test on D2

```{r}
#there is no significant difference between the variances of the two sets of data
ftest2 <- var.test(Personalization_fee_difference ~ group, data = data)
ftest2
```
F test on D3

```{r}
#there is no significant difference between the variances of the two sets of data
ftest3 <- var.test(Fee_personalization ~ group, data = data)
ftest3
```

F test on D4

```{r}
#there is no significant difference between the variances of the two sets of data
ftest4 <- var.test(Fee_without_personalization ~ group, data = data)
ftest4
```

2 Sample t-test on D2

```{r}
HB_ttest2 <-t.test(Personalization_fee_difference  ~ group, data = data, var.equal=T)
HB_ttest2
```

Welch sample t-test on D2

```{r}
HB_ttest3 <-t.test(Personalization_fee_difference   ~ group, data = data)
HB_ttest3

```


Welch sample t-test on D3

```{r}
#No statistically significant difference between control and treatment groups
HB_ttest4 <-t.test(Fee_personalization ~ group, data = data)
HB_ttest4
```
Welch sample t-test on D4

```{r}
#No statistically significant difference between control and treatment groups
HB_ttest5 <-t.test(Fee_without_personalization ~ group, data = data)
HB_ttest5
```


Visualization on D3, D4, D11 for supporting the test on HB

```{r}
data %>% group_by(group, equal_fee) %>% summarise(count=n()) %>% ggplot(aes(x = equal_fee, y=count, fill=group))+
  geom_bar(stat='identity', position="dodge") +
  labs(x = "Service Type", y = "Number of people",
       title = "Which User Should Pay a Higher Service Fee?", caption="User A opts in for personalziation while User B opts out")+
  theme_minimal()+scale_fill_grey()+
    geom_text(
    aes(label = count),
    colour = "black", size = 0.5,
    vjust = 0.1, position = position_dodge(.9)) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```

Table on treatment and control summaries for D2, D3, D4

```{r}
data %>% group_by(group) %>% summarise('Default Fee Answer'=mean(fee),'Fee with Personalization'=mean(Fee_personalization), 'Fee without Personalization'=mean(Fee_without_personalization,), 'Difference of User A and B'=mean(Personalization_fee_difference)) 
```

**Reconstructing Control and Treatment Groups Based on Understanding Check**

Do control and treatment people have different opinions on whether their data is used for others or not?

```{r}
data %>% group_by(group, understand_other) %>% summarise(count=n()) %>% ggplot(aes(x = understand_other, y=count, fill=group))+
  geom_bar(stat='identity', position="dodge") +
  labs(x = "Answers by Treatment and Control Groups", y = "Number of people",
       title = "Is your data used to recommend songs to others?", caption="Expected answers: Treatment:no, Control:yes")+
  theme_minimal()+scale_fill_grey()+
    geom_text(
    aes(label = count),
    colour = "black", size = 3,
    vjust = 0.1, position = position_dodge(.9)) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```

Copying the data file in order to reconstruct the control and treatment groups based on the understanding check

```{r}
reconst <- data
```

```{r}
#reconstructing control and treatment groups based on answers to understanding checks
reconst <- reconst %>% 
  mutate("reconst_groups" = if_else((understand_you == "Yes" & understand_other =="Yes"), "reconst_treatment",if_else(understand_you=="Yes" & understand_other=="No", "reconst_control","ignore"))) %>% filter(reconst_groups!="ignore")
```

```{r}
#summary of new control and treatment groups
reconst %>% group_by(reconst_groups) %>% summarise(count=n(),fee=mean(fee),sd_fee=sd(fee),diff_fee=mean(Personalization_fee_difference),sd_diff=sd(Personalization_fee_difference),pers_fee=mean(Fee_personalization),sd_pers=sd(Fee_personalization),without_fee=mean(Fee_without_personalization),sd_without=sd(Fee_without_personalization))
```


F-test on the reconstructed group

```{r}
ftest5 <- var.test(fee ~ group, data = reconst)
ftest5
```


1) Testing HA with reconstructed groups

2 sample t-test ADD HERE F TEST TOO

```{r}
#no statistically significant difference
HA_reconst_ttest <-t.test(fee ~ reconst_groups, data = reconst)
HA_reconst_ttest
```


2) Testing HB with reconstructed groups

F test on D2
```{r}
ftest5 <- var.test(Personalization_fee_difference ~ group, data = reconst)
ftest5
```


Welch on D2

```{r}
#statistically significant difference is found between treatment and control
HB_reconst_ttest <-t.test(Personalization_fee_difference ~ reconst_groups, data = reconst)
HB_reconst_ttest
```

Welch on D3

```{r}
#statistically significant difference is found between treatment and control
HB_reconst_ttest2 <-t.test(Fee_personalization ~ reconst_groups, data = reconst)
HB_reconst_ttest2
```
Welch on D4

```{r}
#statistically significant difference is found between treatment and control
HB_reconst_ttest3 <-t.test(Fee_without_personalization~ reconst_groups, data = reconst)
HB_reconst_ttest3
```

```{r}
reconst %>% group_by(reconst_groups) %>% summarize("Average fee with personalization"=mean(Fee_personalization), "Average fee without personalization"=mean(Fee_without_personalization), "Difference"=mean(Personalization_fee_difference))
```


**Further Analysis: Logistic regression on the dependent variables**


Creating binary variables for logistic regression

Data preparation: 

```{r}
logistic <- data
```

```{r}
logistic$fee_binary[logistic$fee < mean(logistic$fee)] <- 0
logistic$fee_binary[logistic$fee >= mean(logistic$fee)] <- 1
logistic$fee_usera_binary[logistic$Fee_personalization < mean(logistic$Fee_personalization)] <- 0
logistic$fee_usera_binary[logistic$Fee_personalization >= mean(logistic$Fee_personalization)] <- 1
logistic$fee_userb_binary[logistic$Fee_without_personalization < mean(logistic$Fee_without_personalization)] <- 0
logistic$fee_userb_binary[logistic$Fee_without_personalization >= mean(logistic$Fee_without_personalization)] <- 1
logistic$fee_aminusb_binary[logistic$Personalization_fee_difference < mean(logistic$Personalization_fee_difference)] <- 0
logistic$fee_aminusb_binary[logistic$Personalization_fee_difference >= mean(logistic$Personalization_fee_difference)] <- 1
```

```{r}
logistic$benefit_1_binary <- ifelse(logistic$benefit_1 < mean(logistic$benefit_1), 0, 1)
logistic$benefit_4_binary <- ifelse(logistic$benefit_4 < mean(logistic$benefit_4), 0, 1)
logistic$benefit_5_binary <- ifelse(logistic$benefit_5 < mean(logistic$benefit_5), 0, 1)
logistic$preferences_1_binary <- ifelse(logistic$preferences_1 < mean(logistic$preferences_1), 0, 1)
logistic$preferences_4_binary <- ifelse(logistic$preferences_4 < mean(logistic$preferences_4), 0, 1)
logistic$preferences_5_binary <- ifelse(logistic$preferences_5 < mean(logistic$preferences_5), 0, 1)
```

Data summary:

```{r}
summary(logistic)
```

Logistic Regression Models - Below 10 models are all models before simplifying the models based on statistical significance. The simplification process is explained under the "Model Selection" section.

```{r}
log1 <- glm(fee_binary ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political) + benefit_1+benefit_4+benefit_5+preferences_1+preferences_4+preferences_5, data=logistic, family="binomial")
summary(log1)
```

```{r}
log5 <- glm(benefit_1_binary ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political) +benefit_4+benefit_5+preferences_1+preferences_4+preferences_5, data=logistic, family="binomial")
summary(log5)
```

```{r}
log8 <- glm(preferences_1_binary ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political) +benefit_4+benefit_5+preferences_4+preferences_5, data=logistic, family="binomial")
summary(log8)
```

```{r}
log10 <- glm(preferences_5_binary ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political) +benefit_4+benefit_5+preferences_4+preferences_1, data=logistic, family="binomial")
summary(log10)
```

```{r}
log2 <- glm(fee_usera_binary ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political) + benefit_1+benefit_4+benefit_5+preferences_1+preferences_4+preferences_5, data=logistic, family="binomial")
summary(log2)
```

```{r}
log3 <- glm(fee_userb_binary ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political) + benefit_1+benefit_4+benefit_5+preferences_1+preferences_4+preferences_5, data=logistic, family="binomial")
summary(log3)
```

```{r}
log4 <- glm(fee_aminusb_binary ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political) +benefit_4+benefit_5+preferences_1+preferences_4+preferences_5, data=logistic, family="binomial")
summary(log4)

```

```{r}
log6 <- glm(benefit_4_binary ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political) +benefit_1+benefit_5+preferences_1+preferences_4+preferences_5, data=logistic, family="binomial")
summary(log6)
```

```{r}
log7 <- glm(benefit_5_binary ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political) +benefit_4+benefit_1+preferences_1+preferences_4+preferences_5, data=logistic, family="binomial")
summary(log7)
```

```{r}
log9 <- glm(preferences_4_binary ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political) +benefit_4+benefit_5+preferences_1+preferences_5, data=logistic, family="binomial")
summary(log9)
```

Final models referred in the paper after the model selection, following the order in the paper.

```{r}
log1_simplified <- glm(fee_binary ~ as.factor(Income)+benefit_4, data=logistic, family="binomial")
summary(log1_simplified)
```

```{r}
log5_simplified <- glm(benefit_1_binary ~ as.factor(group)+as.factor(Gender)+Personalization_satisfaction + as.factor(Political) +benefit_4+preferences_5, data=logistic, family="binomial")
summary(log5_simplified)
```

```{r}
log8_simplified_V2 <- glm(preferences_1_binary ~ benefit_5+preferences_4+preferences_5, data=logistic, family="binomial")
summary(log8_simplified_V2)
```

```{r}
log10_simplified <- glm(preferences_5_binary ~ Personalization_satisfaction+benefit_1+preferences_1+preferences_4, data=logistic, family="binomial")
summary(log10_simplified)
```

**Linear regression on the dependent variables**

Linear Regression Models - Below 10 models are all models before feature selection in order to simplify the models based on statistical significance.The simplification process is explained under the "Model Selection" section.

```{r}
lm1<- lm(fee ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+Personalization_satisfaction + as.factor(Political) + benefit_1+benefit_4+benefit_5+preferences_1+preferences_4+preferences_5, data=data)
summary(lm1)
```

```{r}
#due to "prefer not to say" answers creating NAs in Income_numeric, we tested Income_numeric and income as factor and found higher R-squared for income as factor. Hence we will introduce income as factorial categorical variables in rest of the models.

lm1_alternative<- lm(fee ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+Personalization_satisfaction + as.factor(Political) + benefit_1+benefit_4+benefit_5+preferences_1+preferences_4+preferences_5, data=data)
summary(lm1_alternative)
```

```{r}
lm5 <-lm(benefit_1 ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political)+benefit_4+benefit_5+preferences_1+preferences_4+preferences_5, data=data, na.rm=T)
summary(lm5)
```

```{r}
lm8 <-lm(preferences_1 ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political)+benefit_4+benefit_5+benefit_1+preferences_4+preferences_5, data=data, na.rm=T)
summary(lm8)
```

```{r}
lm8_alternative <-lm(preferences_1 ~ benefit_5+preferences_4+preferences_5, data=data, na.rm=T)
summary(lm8_alternative)

```

```{r}
lm10 <-lm(preferences_5 ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political)+benefit_4+benefit_5+benefit_1+preferences_4+preferences_1, data=data, na.rm=T)
summary(lm10)
```

```{r}
lm2<- lm(Fee_personalization ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political) + benefit_1+benefit_4+benefit_5+preferences_1+preferences_4+preferences_5, data=data, na.rm=T)
summary(lm2)
```

```{r}
lm3<- lm(Fee_without_personalization ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political) + benefit_1+benefit_4+benefit_5+preferences_1+preferences_4+preferences_5, data=data, na.rm=T)
summary(lm3)
```

```{r}
lm4<- lm(Personalization_fee_difference ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political) + benefit_1+benefit_4+benefit_5+preferences_1+preferences_4+preferences_5, data=data, na.rm=T)
summary(lm4)
```

```{r}
lm6 <-lm(benefit_4 ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political)+benefit_1+benefit_5+preferences_1+preferences_4+preferences_5, data=data, na.rm=T)
summary(lm6)

```

```{r}
lm7<-lm(benefit_5 ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political)+benefit_4+benefit_1+preferences_1+preferences_4+preferences_5, data=data, na.rm=T)
summary(lm7)
```

```{r}
lm9 <-lm(preferences_4 ~ as.factor(group)+Age+as.factor(Gender)+Education_numeric+as.factor(Income)+Using_PSPs+Using_Spotify+ +Personalization_satisfaction + as.factor(Political)+benefit_4+benefit_5+benefit_1+preferences_1+preferences_5, data=data, na.rm=T)
summary(lm9)
```

Final models referred in the paper after the feature selection, following the order in the paper:

```{r}
lm1_simplified<- lm(fee ~ as.factor(Income)+benefit_4, data=data)
summary(lm1_simplified)
```

```{r}
lm5_simplified<- lm(benefit_1 ~ as.factor(group)+as.factor(Gender)+Personalization_satisfaction + as.factor(Political)+benefit_4+preferences_5, data=data, na.rm=T)
summary(lm5_simplified)
```

```{r}
lm8_simplified_V2 <-lm(preferences_1 ~ benefit_5+preferences_4+preferences_5, data=data, na.rm=T)
summary(lm8_simplified_V2)
```

```{r}
lm10_simplified <-lm(preferences_5 ~ Personalization_satisfaction+ benefit_1+preferences_1+preferences_4, data=data, na.rm=T)
summary(lm10_simplified)
```

**Model Simplification**

Following the order in the paper, below models were referred in the results

LM1 simplified to significantly variables only.The multiple R squared has decreased from 7.4% to 3.7%.

```{r}
lm1_simplified<- lm(fee ~ as.factor(Income)+benefit_4, data=data)
summary(lm1_simplified)
```

According to ANOVA analysis, the larger model does not perform significantly better than the simpler model, hence we move forward with the simpler model. 

```{r}
anova(lm1,lm1_simplified)
```

LM5 simplified to significantly variables only.The multiple R squared has dropped only slightly from 39.87% to 39.2%.

```{r}
lm5_simplified<- lm(benefit_1 ~ as.factor(group)+as.factor(Gender)+Personalization_satisfaction + as.factor(Political)+benefit_4+preferences_5, data=data, na.rm=T)
summary(lm5_simplified)
```

According to ANOVA analysis, the larger model does not perform significantly better than the simpler model, hence we move forward with the simpler model. 


```{r}
anova(lm5,lm5_simplified)
```

LM8 simplified to significantly variables only. Age variable was found statistically insignificant in the new model. Age has dropped in the further simplified model. The multiple R squared has dropped from 26.1% to 23.5%. 

```{r}
lm8_simplified <-lm(preferences_1 ~ Age+ benefit_5+preferences_4+preferences_5, data=data, na.rm=T)
summary(lm8_simplified)
```


```{r}
lm8_simplified_V2 <-lm(preferences_1 ~ benefit_5+preferences_4+preferences_5, data=data, na.rm=T)
summary(lm8_simplified_V2)
```

According to ANOVA analysis, the larger model does not perform significantly better than the simpler model, hence we move forward with the simpler model. 

```{r}
anova(lm8,lm8_simplified_V2)
```

LM10 simplified to significantly variables only. The multiple R squared has dropped from 28.6% to 26.7%. 

```{r}
lm10_simplified <-lm(preferences_5 ~ Personalization_satisfaction+ benefit_1+preferences_4+preferences_1, data=data, na.rm=T)
summary(lm10_simplified)
```

According to ANOVA analysis, the larger model does not perform significantly better than the simpler model, hence we move forward with the simpler model. 

```{r}
anova(lm10,lm10_simplified)
```


**Latex Conversions**

Full versions as a back up, not used in the paper:

```{r}
stargazer(lm1, log1, lm5, log5, title="Regression Models on D1 and D5",
align=TRUE, dep.var.labels=c("D1","Binary D1", "D5","Binary D5"),
omit.stat=c("LL","ser","f"), no.space=TRUE)
```


```{r}
stargazer(lm8,log8, lm10,log10, title="Regression Models on D8 and D10",
align=TRUE, dep.var.labels=c("D8","Binary D8","D10","Binary D10"),
omit.stat=c("LL","ser","f"), no.space=TRUE)
```


Simplified final models, used in the paper:

```{r}
stargazer(lm1_simplified, log1_simplified, lm5_simplified, log5_simplified, title="Regression Models on Y1 and Y5",
align=TRUE, dep.var.labels=c("Y1","Binary Y1", "Y5","Binary Y5"),
omit.stat=c("LL","ser","f"), no.space=TRUE)
```


```{r}
stargazer(lm8_simplified_V2,log8_simplified_V2, lm10_simplified,log10_simplified, title="Regression Models on Y8 and Y10",
align=TRUE, dep.var.labels=c("Y8","Binary Y8","Y10","Binary Y10"),
omit.stat=c("LL","ser","f"), no.space=TRUE)
```
